Gut microbes and their genes are associated with cognition and neuroanatomy in children

### 2023-02-28 manuscript/main.tex
update title / authors, fix table 1
Incorporated tables 3-5 into main.tex

\title{Gut microbes and their genes or something else}

@@

@@

@@

>>>>

\title{Gut microbes and their genes are associated with cognition and neuroanatomy in children}

@@

\begin{table}
    \begin{tabular}{rrrrr}
      \hline\hline
      \textbf{Subject Ages (months)} & \textbf{Microbial feature} & \textbf{Demo.} & \textbf{Test set correlation (± C.I.)} & \textbf{Test set Root-mean-square error (± C.I.)} \\\hline
      0 to 6 & - & + & 13.01 ± 0.05 & -0.14 ± 0.01 \\
      0 to 6 & taxa & - & 12.66 ± 0.05 & -0.1 ± 0.01 \\
      0 to 6 & taxa & + & 12.7 ± 0.05 & -0.12 ± 0.01 \\
      0 to 6 & genes & - & 12.56 ± 0.05 & -0.01 ± 0.01 \\
      0 to 6 & genes & + & 12.56 ± 0.05 & -0.02 ± 0.01 \\
      18 to 120 & - & + & 16.27 ± 0.04 & 0.506 ± 0.003 \\
      18 to 120 & taxa & - & 17.66 ± 0.04 & 0.363 ± 0.003 \\
      18 to 120 & taxa & + & 17.29 ± 0.04 & 0.429 ± 0.003 \\
      18 to 120 & genes & - & 18.01 ± 0.04 & 0.303 ± 0.003 \\
      18 to 120 & genes & + & 17.86 ± 0.04 & 0.333 ± 0.004 \\\hline\hline
    \end{tabular}
\end{table}

@@

\begin{table}
    \begin{tabular}{rrr}
      \hline\hline
      \textbf{Statistic} & \textbf{Mean absolute proportional error (MAPE)} & \textbf{Correlation coefficient (R)} \\\hline
      Mean & 0.073 & 0.137 \\
      Standard deviation & 0.028 & 0.137 \\
      Maximum & 0.206 & 0.605 \\
      75th percentile & 0.082 & 0.195 \\
      50th percentile & 0.067 & 0.134 \\
      25th percentile & 0.057 & 0.062 \\
      Minimum & 0.035 & -0.147 \\\hline\hline
    \end{tabular}
\end{table}

@@

\begin{table}
    \begin{tabular}{rrrr}
      \hline\hline
      \textbf{Input set} & \textbf{Age bracket} & \textbf{Microbiome encoding type} & \textbf{Demographics Provided? (sex, education)} \\\hline
      1 & 0 to 6 months & Not provided & yes \\
      2 & 0 to 6 months & Taxonomic profile & no \\
      3 & 0 to 6 months & Taxonomic profile & yes \\
      4 & 0 to 6 months & Functional Profile (ECs) & no \\
      5 & 0 to 6 months & Functional Profile (ECs) & yes \\
      6 & 18 to 120 months & Not provided & yes \\
      7 & 18 to 120 months & Taxonomic profile & no \\
      8 & 18 to 120 months & Taxonomic profile & yes \\
      9 & 18 to 120 months & Functional Profile (ECs) & no \\
      10 & 18 to 120 months & Functional Profile (ECs) & yes \\\hline\hline
    \end{tabular}
\end{table}
